---
title: "Git-Repository Analysis"
output:
    github_document:
        toc: true
        toc_depth: 4
---


## Introduction

### Context
- Knowledge Management | Project Paper


### Authors

- [70415245 | Lisa Rosenberg](https://github.com/lisa-rosenberg)
- [70428153 | Dmitrij Drandarov](https://github.com/dmitrij-drandarov)



## Setup

### Tools
- [Neo4j](https://neo4j.com/)
- [jQAssistant](https://github.com/buschmais/jqassistant)
- [jQAssistant Git-Plugin](https://github.com/kontext-e/jqassistant-plugins/blob/master/git/src/main/asciidoc/git.adoc)


### Instructions

- Fügen Sie das jQAssistant-Plugin in die pom.xml Ihres Maven-Projekts ein

```{xml}
<build>
    <plugins>
        <plugin>
            <groupId>com.buschmais.jqassistant</groupId>
            <artifactId>jqassistant-maven-plugin</artifactId>
            <version>${jqassistant-maven-plugin.version}</version>
            <extensions>true</extensions>
            <executions>
                <execution>
                    <goals>
                        <goal>scan</goal>
                        <goal>analyze</goal>
                    </goals>
                    <configuration>
                        <scanIncludes>
                            <scanInclude>
                                <path>${project.basedir}/.git</path>
                            </scanInclude>
                        </scanIncludes>
                    </configuration>
                </execution>
            </executions>
            <dependencies>
                <dependency>
                    <groupId>de.kontext-e.jqassistant.plugin</groupId>
                    <artifactId>jqassistant.plugin.git</artifactId>
                    <version>1.2.0</version>
                </dependency>
            </dependencies>
        </plugin>
    </plugins>
</build>
```

- Führen Sie folgende Maven-Befehle aus:

```
mvn install
mvn jqassistant:server
```

- Öffnen Sie http://localhost:7474 in Ihrem Browser zum Zugriff auf die Neo4j Datenbank

- Führen Sie nach Belieben Cypher-Queries aus. Die Ergebnisse lassen sich als csv-Dateien exportieren und z.B. mit R analysieren



## Analysis

```{r libraries, include=FALSE, echo=TRUE}
# # Packages
# Install packages (uncomment to install packages on initial run :) )
#install.packages("zoo")
#install.packages("ggplot2")
#install.packages("scales")
#install.packages("gridExtra")
#install.packages("plyr")
#install.packages("vcd")
#install.packages("tm")
#install.packages("wordcloud")
#install.packages("SnowballC")
# Load libraries
library(zoo)
library(ggplot2)
library(RColorBrewer)
library(scales)
library(gridExtra)
library(plyr)
library(vcd)
library(tm)
library(wordcloud)
library(SnowballC)

# # Set variables
palette <- "Dark2"  # ggplot palette name
wrapAtChar <- 25    # wrap label names
maxFiles <- 25      # number of most changed files

# # Set functions
getPalette <- colorRampPalette(brewer.pal(7, palette))
```

Git kodiert verschiedene Modifikationen von Dateien als Buchstaben. Unten sieht man eine Auflistung aller möglichen Werte mit ihrer jeweiligen bedeutung.

- A → Added
- C → Copied
- D → Deleted
- M → Modified
- R → Renamed
- T → Have their type (mode) changed
- U → Unmerged
- X → Unknown
- B → Have had their pairing Broken



### Changes in Repository

#### Change Count by Modification Kind
```{java}
MATCH (author:Author)-[COMMITED]->(commit:Commit)-[CONTAINS_CHANGE]->(change:Change)-[MODIFIES]->(file:File)
RETURN change.modificationKind AS ModificationKind, count(change.modificationKind) AS ChangeCount
  ORDER BY ChangeCount DESC
```

```{r change-count-by-modification-kind, fig.width=7.5, fig.height=7.5}
# # Load data
csv <- read.table(file.path("../../result/dukecon/Change-Count.csv"), sep=",", header=TRUE)

# # Setup plot
slices <- c(csv$ChangeCount)
percentage <- round(slices/sum(slices)*100)
labels <- csv$ModificationKind
labels <- paste(labels, " (", slices, " | ", percentage, "%)", sep="")
colors <- brewer.pal(max(as.numeric(csv$ModificationKind)), palette)

# # Display plot
pie(slices, labels=labels, col=colors, main="Change Count by Modification Kind")
```


#### Change Count by Modification Kind and Authors
```{java}
MATCH (author:Author)-[COMMITED]->(commit:Commit)-[CONTAINS_CHANGE]->(change:Change)-[MODIFIES]->(file:File)
RETURN author.name AS Author, change.modificationKind AS ModificationKind
    ORDER BY ModificationKind, Author
```

```{r change-count-by-modification-kind-and-author, fig.width=10, fig.height=10}
# # Load data
csv <- read.table(file.path("../../result/dukecon/wip/Change-Count-by-Author.csv"), sep=",", header=TRUE)

# # Filter data
percentage <- nrow(csv)/100
table <- table(csv$Author, csv$ModificationKind)
subset <- table[table(csv$Author)>percentage,]

# # Setup plot
colors <- brewer.pal(max(as.numeric(csv$ModificationKind)), palette)

# # Display plot
mosaicplot(subset, col=colors, las=3, ylab="ModificationKind", main="Change Count by Modification Kind and Authors", cex.axis=0.8, mar=c(0,0,0,0), pop=FALSE)
```



### Changes by Time

#### Change Count by Month
```{java}
MATCH (author:Author)-[COMMITED]->(commit:Commit)-[CONTAINS_CHANGE]->(change:Change)-[MODIFIES]->(file:File)
RETURN split(commit.date,'-')[0]+'-'+split(commit.date,'-')[1] AS CommitDate, change.modificationKind AS ModificationKind, count(change) AS ChangeCount
  ORDER BY ModificationKind, CommitDate, ChangeCount DESC
```

```{r change-count-by-month, fig.width=10, fig.height=10}
# # Load data
csv <- read.table(file.path("../../result/dukecon/wip/Change-Count-by-Date-Month.csv"), sep=",", header=TRUE)

# # Filter data
subset1 <- aggregate(ChangeCount ~ CommitDate, csv, sum)

# # Transform data
numModificationKind <- as.numeric(csv$ModificationKind) 
xrange <- range(as.yearmon(subset1$CommitDate))
yrange <- range(subset1$ChangeCount)

# # Setup plot
plot(xrange, yrange, type="n", xlab="", ylab="ChangeCount", main="Change Count by Month", cex.axis=0.8, mar=c(0,3.8,1.5,0), xaxt='n')
axis(side=1, las=2, labels=c(as.yearmon(csv$CommitDate)), at=c(as.yearmon(csv$CommitDate)))
abline(v=(c(as.yearmon(csv$CommitDate))), col="grey", lty="dotted")
colors <- brewer.pal(max(as.numeric(csv$ModificationKind)), palette)
plotchar <- seq(18, 18 + max(numModificationKind), 1)

# # Display plot
lines(as.yearmon(subset1$CommitDate), subset1$ChangeCount, type="h", lwd=10, col="gray27")
for (i in 1:max(numModificationKind)) { 
  x <- subset(csv, numModificationKind==i)
  lines(as.yearmon(x$CommitDate), x$ChangeCount, type="l", lwd=2, col=colors[i], pch=plotchar[i])
}

# # Display legend
legend(xrange[1], yrange[2], unique(csv$ModificationKind), cex=0.8, col=colors, lty=1, title="ModKind")
```


#### Change Count by Month and Authors
```{java}
MATCH  (author:Author)-[COMMITED]->(commit:Commit)-[CONTAINS_CHANGE]->(change:Change)-[MODIFIES]->(file:File)
RETURN author.name AS Author, split(commit.date,'-')[0]+'-'+split(commit.date,'-')[1] AS CommitDate, change.modificationKind AS ModificationKind, count(change) AS ChangeCount
  ORDER BY CommitDate, ChangeCount DESC, ModificationKind
```

```{r change-counts-of-falk-sippach, fig.width=10, fig.height=10}
# # Load data
csv <- read.table(file.path("../../result/dukecon/wip/Change-Count-by-Author-by-Date-Month.csv"), sep=",", header=TRUE)

# # Filter data
subset1 <- subset(csv, Author == "Falk Sippach", select = -c(ModificationKind))
subset1 <- aggregate(ChangeCount ~ CommitDate, subset1, sum)
subset2 <- subset(csv, Author == "Falk Sippach")

# # Transform data
numModificationKind <- as.numeric(subset2$ModificationKind)
xrange <- range(as.yearmon(subset1$CommitDate))
yrange <- range(subset1$ChangeCount)

# # Setup plot
plot(xrange, yrange, type="n", xlab="", ylab="ChangeCount", main="Change Counts of Falk Sippach by Month", cex.axis=0.8, mar=c(0,3.8,1.5,0), xaxt='n')
axis(side=1, las=2, labels=c(as.yearmon(subset1$CommitDate)), at=c(as.yearmon(subset1$CommitDate)))
abline(v=(c(as.yearmon(subset1$CommitDate))), col="grey", lty="dotted")
colors <- brewer.pal(max(as.numeric(csv$ModificationKind)), palette)
plotchar <- seq(18, 18 + max(numModificationKind), 1)

# # Display plot
lines(as.yearmon(subset1$CommitDate), subset1$ChangeCount, type="h", lwd=10, col="gray27")
for (i in 1:max(numModificationKind)) { 
  x <- subset(subset2, numModificationKind==i)
  lines(as.yearmon(x$CommitDate), x$ChangeCount, type="l", lwd=2, col=colors[i], pch=plotchar[i])
}

# # Display legend
legend(xrange[1], yrange[2], c("A", "C", "D", "M", "R"), cex=0.8, col=colors, lty=1, title="ModKind")
```



### Changes by File Type

#### Change Count by File Type
```{java}
MATCH (change:Change)-[MODIFIES]->(file:File)
WITH split(file.relativePath, '.')[1] AS FileType, change
  WHERE FileType <> 'null' AND NOT(FileType CONTAINS '/')
RETURN FileType, count(change) AS ChangeCount
  ORDER BY ChangeCount DESC, FileType
```

```{r change-count-by-file-type, fig.width=10, fig.height=15}
# # Load data
csv <- read.table(file.path("../../result/dukecon/wip/Change-Count-by-File-Type.csv"), sep=",", header=TRUE)

# # Setup plot
colorCount <- max(as.numeric(csv$FileType))
ymax <- round_any(max(csv$ChangeCount)*120/100, 10, f=ceiling)

# # Display plot
ggplot(csv, aes(x=reorder(FileType, ChangeCount), y=ChangeCount)) +
  geom_bar(stat="identity", fill=getPalette(colorCount)) + coord_flip() +
  geom_text(aes(label=ChangeCount), vjust=0.5, hjust=-0.5, size=3) +
  theme(axis.title=element_text(size=7.5,face="bold"), title=element_text(size=7.5,face="bold")) +
  scale_y_continuous(limits=c(0, 1050), expand=c(0, 0)) +
  labs(x="FileType", title="Change Count by File Type")
```


#### Change Count by File Type and Authors
```{java}
MATCH (author:Author)-[COMMITED]->(commit:Commit)-[CONTAINS_CHANGE]->(change:Change)-[MODIFIES]->(file:File)
WITH change.modificationKind AS ModificationKind, author.name AS Author, split(file.relativePath, '.')[1] AS FileType
  WHERE NOT(FileType CONTAINS '/')
RETURN Author, FileType
  ORDER BY Author, FileType
```

```{r change-counts-of-author-by-file-type, fig.width=10, fig.height=10}
# # Load data
csv <- read.table(file.path("../../result/dukecon/wip/Change-Count-by-File-Type-by-Author.csv"), sep=",", header=TRUE)

# # Filter data
subset1 <- subset(csv, Author=="Falk Sippach")
subset2 <- subset(csv, Author=="Alexander Schwartz")

# # Transform data
ymax1 <- round_any(max(table(subset1$FileType))*120/100, 10, f=ceiling)
ymax2 <- round_any(max(table(subset2$FileType))*120/100, 10, f=ceiling)

# # Setup plot
colorCount1 <- max(as.numeric(droplevels.factor(subset1[2>0]$FileType)))
colorCount2 <- max(as.numeric(droplevels.factor(subset2[2>0]$FileType)))

# # Display plot
plot1 <- ggplot(subset1, aes(x=factor(FileType))) +
  geom_bar(fill=getPalette(colorCount1)) +
  geom_text(stat='count', aes(label=..count..), hjust=-0.5, size=2, angle=90) +
  scale_y_continuous(limits=c(0, ymax1), expand=c(0, 0)) +
  theme(axis.text.x=element_text(angle=90, hjust=1, vjust=0.30), axis.title=element_text(size=7.5,face="bold"), title=element_text(size=7.5,face="bold")) +
  labs(x="", y="ChangeCount", title="Change Counts of Falk Sippach by File Type")

plot2 <- ggplot(subset2, aes(x=factor(FileType))) +
  geom_bar(fill=getPalette(colorCount2)) +
  geom_text(stat='count', aes(label=..count..), hjust=-0.5, size=2, angle=90) +
  scale_y_continuous(limits=c(0, ymax2), expand=c(0, 0)) +
  theme(axis.text.x=element_text(angle=90, hjust=1, vjust=0.30), axis.title=element_text(size=7.5,face="bold"), title=element_text(size=7.5,face="bold")) +
  labs(x="", y="ChangeCount", title="Change Counts of Alexander Schwartz by File Type")

grid.arrange(plot1, plot2, nrow=2)
```



### Ownership of Repository

#### Ownership of Repository by File Types and Authors
```{java}
MATCH (author:Author)-[COMMITED]->(commit:Commit)-[CONTAINS_CHANGE]->(change:Change)-[MODIFIES]->(file:File)
WITH change.modificationKind AS ModificationKind, author.name AS Author, split(file.relativePath, '.')[1] AS FileType
RETURN Author, count(ModificationKind), ModificationKind, FileType
  ORDER BY ModificationKind, count(ModificationKind) DESC, Author
```

```{r ownership-of-repository-of-author-by-file-types, fig.width=10, fig.height=10}
# # Load data
csv <- read.table(file.path("../../result/dukecon/wip/Change-Count-by-File-Type-by-Author.csv"), sep=",", header=TRUE)
  
# # Filter data
subset1 <- subset(csv, Author=="Falk Sippach")
subset2 <- subset(csv, Author=="Alexander Schwartz")

# # Transform data
proportion1 <- round(table(subset1$FileType)/table(csv$FileType)*100, digits=2)
proportion2 <- round(table(subset2$FileType)/table(csv$FileType)*100, digits=2)

# # Setup plot
colorCount <- max(as.numeric(csv$FileType))

# # Display plot
plot1 <- ggplot(data.frame(proportion1), aes(x=Var1, y=Freq)) +
  geom_bar(stat="identity", fill=getPalette(colorCount)) +
  geom_text(aes(label=paste(Freq, "%")), hjust=-0.25, size=2, angle=90) +
  scale_y_continuous(limits=c(0,100), expand=c(0, 0)) +
  theme(axis.text.x=element_text(angle=90, hjust=1, vjust=0.30), axis.title=element_text(size=7.5,face="bold"), title=element_text(size=7.5,face="bold")) +
  labs(x="", y="ChangeCount in %", title="Ownership of Repository of Falk Sippach by File Types")

plot2 <- ggplot(data.frame(proportion2), aes(x=Var1, y=Freq)) +
  geom_bar(stat="identity", fill=getPalette(colorCount)) +
  geom_text(aes(label=paste(Freq, "%")), hjust=-0.25, size=2, angle=90) +
  scale_y_continuous(limits=c(0,100), expand=c(0, 0)) +
  theme(axis.text.x=element_text(angle=90, hjust=1, vjust=0.30), axis.title=element_text(size=7.5,face="bold"), title=element_text(size=7.5,face="bold")) +
  labs(x="", y="ChangeCount in %", title="Ownership of Repository of Alexander Schwartz by File Types")

grid.arrange(plot1, plot2, nrow=2)
```


#### Ownership of Repository by Packages
```{java}
MATCH (author:Author)-[COMMITED]->(commit:Commit)-[CONTAINS]->(change:Change)-[MODIFIES]->(file:File)
WITH file, change, author.name AS Author,
     split(file.relativePath, '/')[0] + '/' AS Path
  WHERE NOT(Path CONTAINS '.')
RETURN Author, count(change) AS ChangeCount, Path
  ORDER BY Path, ChangeCount DESC

UNION
MATCH (author:Author)-[COMMITED]->(commit:Commit)-[CONTAINS]->(change:Change)-[MODIFIES]->(file:File)
WITH file, change, author.name AS Author,
     split(file.relativePath, '/')[0] + '/' +
     split(file.relativePath, '/')[1] + '/' AS Path
  WHERE NOT(Path CONTAINS '.')
RETURN Author, count(change) AS ChangeCount, Path
  ORDER BY Path, ChangeCount DESC

UNION ...
```

```{r ownership-of-authors-by-most-relevant-packages, fig.width=10, fig.height=15}
# # Load data
data <- read.table(file.path("../../result/dukecon/starred/Change-Count-by-Author-by-Package.csv"), sep=",", header=TRUE)

# # Filter data
# Get only packages with more than 1% changes of the repository
maxFiles <- 25 # number of most changed files
temp <- aggregate(ChangeCount ~ Path, data, sum) # sum up ChangeCount of every Author
temp <- temp[with(temp, order(-ChangeCount)),] # sort (descending)
temp <- temp[temp$ChangeCount >= temp$ChangeCount[order(temp$ChangeCount, decreasing=TRUE)][maxFiles],] # select top maxFiles
data <- subset(data, Path %in% temp$Path)

# # Transform data
# Add percentage of changes within packages
data$Pct <- round(data$ChangeCount/with(data, ave(ChangeCount, list(Path), FUN = sum))*100, digits=2)

# Select authors that changed the most in each package #
maxChanged <- with(data, tapply(ChangeCount, Path, which.max))
splitPath <- split(data, data$Path)
data <- na.omit(do.call(rbind, lapply(1:length(splitPath), function(i) splitPath[[i]][maxChanged[i],])))
data <- data[order(match(data[,3],temp[,1])),] # Sort data$FilePath by temp$Path to get sorting by most files
# Add character count of FilePath to data
data$Char <- nchar(as.character(data$Path))

# # Display plot
ggplot(data, aes(x=reorder(Path, Pct), y=Pct, fill=Author)) +
  aes(stringr::str_wrap(data$Path, wrapAtChar), data$Char) +
  scale_fill_brewer(palette=palette) +
  geom_bar(stat="identity") +
  geom_text(aes(label=paste(Author, "-", Pct, "%")), hjust=-0.05, size=3.75) +
  coord_flip() +
  scale_y_continuous(limits=c(0,100), expand=c(0, 0)) +
  theme(legend.position="none", axis.text.x=element_text(angle=90, hjust=1, vjust=0.30, size=10), axis.title=element_text(size=7.5,face="bold"), title=element_text(size=10,face="bold")) +
  labs(x="", y="ChangeCount in %", title="Ownership of Authors by most relevant Packages")
```


#### Ownership of Repository by Files
```{java}
MATCH (author:Author)-[COMMITED]->(commit:Commit)-[CONTAINS]->(change:Change)-[MODIFIES]->(file:File)
WITH file, change, author.name AS Author,
     split(file.relativePath, '/')[0] AS FilePath
  WHERE (FilePath CONTAINS '.')
RETURN Author, count(change) AS ChangeCount, FilePath
  ORDER BY FilePath, ChangeCount DESC

UNION
MATCH (author:Author)-[COMMITED]->(commit:Commit)-[CONTAINS]->(change:Change)-[MODIFIES]->(file:File)
WITH file, change, author.name AS Author,
     split(file.relativePath, '/')[0] + '/' +
     split(file.relativePath, '/')[1] AS FilePath
  WHERE (FilePath CONTAINS '.')
RETURN Author, count(change) AS ChangeCount, FilePath
  ORDER BY FilePath, ChangeCount DESC

UNION ...
```

```{r fig.width=10, fig.height=15}
# # Load data
data <- read.table(file.path("../../result/dukecon/starred/Change-Count-by-Author-by-File.csv"), sep=",", header=TRUE)

# # Filter data
# Select the most changed files in the repository
temp <- aggregate(ChangeCount ~ FilePath, data, sum) # sum up ChangeCount of every Author
temp <- temp[with(temp, order(-ChangeCount)),] # sort (descending)
temp <- temp[temp$ChangeCount >= temp$ChangeCount[order(temp$ChangeCount, decreasing=TRUE)][maxFiles],] # select top maxFiles
data <- subset(data, FilePath %in% temp$FilePath) # subset data based on temp

# # Transform data
# Add percentage of changes within packages
data$Pct <- round(data$ChangeCount/with(data, ave(ChangeCount, list(FilePath), FUN = sum))*100, digits=2)

# Select authors that changed the most
maxChanged <- with(data, tapply(ChangeCount, FilePath, which.max)) # Needed
splitPath <- split(data, data$FilePath) # Needed
data <- na.omit(do.call(rbind, lapply(1:length(splitPath), function(i) splitPath[[i]][maxChanged[i],]))) # Select authors
data <- data[order(match(data[,3],temp[,1])),] # Sort data$FilePath by temp$FilePath to get sorting by most files
# Add character count of FilePath to data
data$Char <- nchar(as.character(data$FilePath))

# # Display plot
ggplot(data, aes(x=FilePath, y=Pct, fill=Author)) +
  aes(stringr::str_wrap(data$FilePath, wrapAtChar), data$Char) +
  scale_fill_brewer(palette=palette) +
  geom_bar(stat="identity") +
  geom_text(aes(label=paste(Author, "-", Pct, "%")), hjust=-0.05, size=3.75) +
  coord_flip() +
  scale_y_continuous(limits=c(0,100), expand=c(0, 0)) +
  theme(legend.position="none", axis.text.y=element_text(size=10), axis.text.x=element_text(angle=90, hjust=1, vjust=0.30, size=10), axis.title=element_text(size=7.5,face="bold"), title=element_text(size=10,face="bold")) +
  labs(x="", y="Ownership in %", title="Ownership of Authors by most relevant Files")
```



### Most used Words

#### Word Cloud of Repository
```{cypher}
MATCH (commit:Commit)
WITH collect(commit) AS Commits
RETURN
  collect(DISTINCT
  split(

  replace(replace(replace(replace(replace(replace(replace(replace(replace(replace(replace(replace(replace(replace(
  replace(replace(replace(replace(replace(replace(replace(replace(replace(replace(replace(replace(replace(replace(
  replace(replace(replace(replace(replace(replace(replace(replace(replace(replace(replace(replace(replace(replace(
  replace(

  toUpper(
  reduce(words = '', aCommit IN Commits | words + aCommit.message)
  ),

  '"', ' '), "'", ' '), '#', ' '), ',', ' '), '(', ' '), ')', ' '), '-', ' '), '+', ' '), '…', ' '), ';', ' '),
  '. ', ' '), '?', ' '), '!', ' '),
  ' OF ', ' '), ' THE ', ' '), ' BRANCH ', ' '), ' INTO ', ' '), ' AND ', ' '), ' FOR ', ' '), ' WITH ', ' '),
  ' PULL ', ' '), ' WE ', ' '), ' HAVE ', ' '), ' A ', ' '), ' MORE ', ' '), ' TO ', ' '), ' PRO ', ' '), ' ON ', ' '),
  ' AN ', ' '), ' IT ', ' '), ' SOME ', ' '), ' SIMPLE ', ' '), ' EASY ', ' '), ' FROM ', ' '), ' OUT ', ' '),
  ' IN ', ' '), ' IS ', ' '), ' OR ', ' '), ' THERE ', ' '), ' THEIR ', ' '),
  '   ', ' '), '  ', ' '), ' ', '_')

  , '_')
  ) AS Words
```

```{r fig.width=10, fig.height=5}
# # Load data
data <- Corpus(DirSource(directory="../../result/dukecon/starred/", pattern="Commit-Message-by-most-used-Words.txt"))

# # Filter data
data <- tm_map(data, stripWhitespace)
data <- tm_map(data, tolower)
data <- tm_map(data, removeWords, stopwords("english"))

# # Display word cloud
wordcloud(data, scale=c(5,0.5), max.words=75, random.order=FALSE, rot.per=0.35, use.r.layout=FALSE, colors=brewer.pal(8, "Dark2"))
```


#### Word Cloud of Repository by File Type
```{cypher}
MATCH (commit:Commit)-[CONTAINS_CHANGE]->(change:Change)-[MODIFIES]->(file:File)
WITH collect(commit) AS Commits, change, split(file.relativePath, '.')[1] AS FileType
RETURN
  FileType,
  collect(DISTINCT
  split(

  replace(replace(replace(replace(replace(replace(replace(replace(replace(replace(replace(replace(replace(replace(
  replace(replace(replace(replace(replace(replace(replace(replace(replace(replace(replace(replace(replace(replace(
  replace(replace(replace(replace(replace(replace(replace(replace(replace(replace(replace(replace(replace(replace(
  replace(

  toUpper(
  reduce(words = '', aCommit IN Commits | words + aCommit.message)
  ),

  '"', ' '), "'", ' '), '#', ' '), ',', ' '), '(', ' '), ')', ' '), '-', ' '), '+', ' '), '…', ' '), ';', ' '),
  '. ', ' '), '?', ' '), '!', ' '),
  ' OF ', ' '), ' THE ', ' '), ' BRANCH ', ' '), ' INTO ', ' '), ' AND ', ' '), ' FOR ', ' '), ' WITH ', ' '),
  ' PULL ', ' '), ' WE ', ' '), ' HAVE ', ' '), ' A ', ' '), ' MORE ', ' '), ' TO ', ' '), ' PRO ', ' '), ' ON ', ' '),
  ' AN ', ' '), ' IT ', ' '), ' SOME ', ' '), ' SIMPLE ', ' '), ' EASY ', ' '), ' FROM ', ' '), ' OUT ', ' '),
  ' IN ', ' '), ' IS ', ' '), ' OR ', ' '), ' THERE ', ' '), ' THEIR ', ' '),
  '   ', ' '), '  ', ' '), ' ', '_')

  , '_')
  ) AS WordsByFileType
```

```{r fig.width=10, fig.height=5}
# # Load data
data <- Corpus(DirSource(directory="../../result/dukecon/starred/", pattern="Commit-Message-by-most-used-Words-by-File-Type-java.txt"))

# # Filter data
data <- tm_map(data, stripWhitespace)
data <- tm_map(data, tolower)
data <- tm_map(data, removeWords, stopwords("english"))

# # Display word cloud
wordcloud(data, scale=c(5,0.5), max.words=75, random.order=FALSE, rot.per=0.35, use.r.layout=FALSE, colors=brewer.pal(8, "Dark2"))
```

```{r fig.width=10, fig.height=5}
# # Load data
data <- Corpus(DirSource(directory="../../result/dukecon/starred/", pattern="Commit-Message-by-most-used-Words-by-File-Type-xml.txt"))

# # Filter data
data <- tm_map(data, stripWhitespace)
data <- tm_map(data, tolower)
data <- tm_map(data, removeWords, stopwords("english"))

# # Display word cloud
wordcloud(data, scale=c(5,0.5), max.words=75, random.order=FALSE, rot.per=0.35, use.r.layout=FALSE, colors=brewer.pal(8, "Dark2"))
```